\documentclass[letterpaper,12pt]{article}
\usepackage{apacite,pdfpages,enumitem,fancyhdr,url,graphicx,tabularx,ragged2e,booktabs,caption,epstopdf}
%http://www.ctan.org/tex-archive/biblio/bibtex/contrib/apacite/apacite.pdf
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[onehalfspacing]{setspace}
\pagestyle{fancy}
\setlist{nolistsep}
\setcounter{secnumdepth}{0}
\setlength{\skip\footins}{1.2cm}
\raggedbottom
\widowpenalty=1000
\clubpenalty=1000
\lhead{Methodology}
\rhead{\thepage}
\cfoot{}
\title{Altright Banning Efficacy}
\date{9 July 2017}
\author{Devin Gaffney}
\begin{document}
\maketitle
\doublespacing

\section{Methodology}

This work leverages what is hereafter referred to as the Baumgartner dataset, a corpus of Reddit content that comprises the vast majority of all Submissions and Comments on the Reddit platform \cite{baumgartner2015dataset}. This dataset has been used in numerous publications to date, ranging from studies on user trajectories \cite{tan2015all,fire2016analyzing} to the emergence of ``spin-off'' communities \cite{hessel2015democrats} to analyzing the dynamics of news cycles and the audiences participating in them \cite{horne2017impact}. In this work, we consider the Reddit corpus dated between the beginning of Reddit in June 2006 to several months after the altright subreddit was banned. In this work we aim to address a hierarchy of questions in increasing complexity. First and foremost, from a system administration view, what is the effect of banning a subreddit on the users who participated in that subreddit? To what extent are there discernible patterns behind users who decided to remain on the platform versus users we have not yet observed to return? We can first consider the raw observed traffic generated by these users in order to address this question. Next, for the users that remain, where did they continue to post after the subreddit was banned, and to what degree does that differ from their behavior prior to the exogenous shock? If we consider the 8,985 participants of the altright subreddit as a cluster of users spanning some portion of all of Reddit on a day to day basis, do we observe and increase in the span of this group (e.g. the group atomizes and disperses through the platform having lost a space previously shared by all), or do we see a decrease in that span (e.g. the users become more insular in new or existing subreddits)? 

The above questions require little more than simple aggregations upon the corpus of data. The fundamental unit of aggregation is the subreddits that users post Submissions or Comments to over time. As users post in subreddits, we consider those to be instantiations of a proxy variable that shows some degree of interest in the community they Submit or Comment within. In all of the above questions, we build models based on this intuition alongside several other fields of metadata contained in the corpus to resolve these questions. Moving beyond this simple proxy variable, however, we are interested in gaining, to some degree, a rough sense of the nature of the content that users post. For this, we trained a series of neural networks to detect whether or not a comment was sufficiently similar to comments typically posted in the altright subreddit. By doing so, it is possible to consider the vast scale of data that these users create on other subreddits. Using the subreddit as a rough proxy, it's possible to reasonably presume that when a user posts within a community, they are posting content that falls within the general milieu of content on the subreddit. This work presumes this to a certain degree, but also employs a set of classifiers to determine whether or not content created by the altright community on other subreddits is reflective of the content patterns of the altright. Collectively, these 8,985 users posted at least 1,444,883 million Submissions and 17,092,807 Comments -- only 12,913 and 142,279 of which were posted to the altright subreddit, respectively. By employing a neural net trained to detect whether or not content is indistuinguishable from the altright corpus, we can investigate the majority of their content posted elsewhere, and determine how these users behave outside the altright, before and after the exogneous shock, and also consider that relationship with respect to the structural similarity of other subreddits as compared to the altright.

Finally, building on \cite{barbosa2016averaging}'s work showing that yearly cohorts may differ significantly, we answer the above questions with respect to the year in which they first began to participate on Reddit. Substantively speaking, this makes clear sense -- the altright subreddit was created in 2010 and only gained appreciable traffic in 2016 -- users who had long participated in Reddit prior to that time may have adapted to Reddit's norms in general prior to altright community norms, and so may react differently to the exogenous shock of banning the altright subreddit. For this reason, all metrics are reported in terms of the entire cohort of 8,985 individuals as well as the cohort broken into yearly groups where applicable or useful.

From June 25 2006 to April 29, 2017 8,985 distinct Reddit users posted either a Submission or a Comment to the altright subreddit at least once. Collectively, these users generated 18,537,690 Submissions and Comments across Reddit as a whole. On February 1st, 2017, the altright subreddit was banned \cite{altright2017banned}. Between February 1st, 2017 and April 29, 2017, 1,821,117 Comments were posted by these individuals as per the Baumgartner dataset. Zero submissions were recorded, likely owing to data errors as elucidated in forthcoming work by Nate Matias and one of the authors that shows gaps in the existing Baumgartner dataset. Due to this paucity of Submission-level data, this work focuses on Comments, which in addition to being accessible, are also more discursive by their nature and likely provide more useful insight into where users interests lie.
\bibliographystyle{apacite}
\bibliography{biblio}
\clearpage
\end{document}